### 2023-01-17 source/paper/main.tex
#16 Additional summary stats
Add additional UCR data, fix weights and event study
Data cleaning, paper reorg, R package

\section*{Figures}

@@

\includegraphics[width=0.7\textwidth]{pretrends/1986/college_enroll_bydrugarrests_1986.png}

\includegraphics[width=0.7\textwidth]{pretrends/2010/college_enroll_bydrugarrests_2010.png}

\includegraphics[width=0.7\textwidth]{eventstudy/high_drug_use/high_marijuana_eventstudy_1986.png}

\includegraphics[width=0.7\textwidth]{eventstudy/high_drug_use/high_marijuana_eventstudy_2010.png}

\section*{Tables}
\import{../../output/tables/}{britton_summ_stats.tex}

>>>>

@@

\begin{figure}[h]
  \caption{College enrollment overtime 1986}
  \centering
  \includegraphics[width=1\textwidth]{pretrends/1986/college_enroll_bydrugarrests_1986.png}
  \label{fig:TBD}
\end{figure}

\begin{figure}[h]
  \caption{College enrollment overtime 2010}
  \centering
  \includegraphics[width=1\textwidth]{pretrends/2010/college_enroll_bydrugarrests_2010.png}
  \label{fig:TBD}
\end{figure}

\begin{figure}[h]
  \caption{Event study 1986, AB arrest rate 18F}
  \centering
  \includegraphics[width=1\textwidth]{eventstudy/high_drug_use/high_marijuana_eventstudy_1986.png}
  \label{fig:TBD}
\end{figure}

\begin{figure}[h]
  \caption{Event study 2010, AB arrest rate 18F}
  \centering
  \includegraphics[width=1\textwidth]{eventstudy/high_drug_use/high_marijuana_eventstudy_2010.png}
  \label{fig:TBD}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%TABLES%%%%%%%%%%%%%%%%%%%%%%%%%%%

\import{../../output/tables/summ_stats/}{cps_summ_stats.tex}
\import{../../output/tables/summ_stats/}{ucr_summ_stats.tex}
